flowers-pilot-analysis

### 2021-08-31 code/aa-flowers-pilot_analysis.Rmd
add player points fig

Rename conditions for readability
```{r}
d.games <- d.games %>% mutate(conditionName = condition, 
                              condition = case_when(condition == "coopMulti" ~ "Cooperative",
                                         condition == "competCartel" ~ "Competitive",
                                         condition == "coopCartel" ~ "Old Cooperative"))
d.games
```

@@

## Simple Distributions
### Points

@@

>>>>

Rename conditions for readability
```{r}
d.games <- d.games %>% mutate(conditionName = condition, 
                              condition = case_when(condition == "coopMulti" ~ "Cooperative",
                                         condition == "competCartel" ~ "Competitive",
                                         condition == "coopCartel" ~ "Old Cooperative",
                                         TRUE ~ condition))
d.games
```

@@

## Deference
How often does a player select a "lower ranked" target?
* Get the rankings of the flowers _visible_ to each participant
** Need a set of rows with each flower visible to each participant and the flower utilities, arrange by utility (grouped by trial and participant ID), assign 1-4 ranking, drop flowers that werent selected

NB: What about cases where a participant selected a flower hidden from them? If we drop both the flowers that are hidden and the flowers that arent selected, we wont have a selection for that trial

[] fix roundId

```{r deference}
trial_deference <- d.by_player_metrics %>% 
  rename(roundID = "_id") %>% 
  full_join(d.contexts %>% 
              select(roundID, blinded, label, utility)) %>%
  filter(blinded != playerId) %>%
  group_by(playerId, roundID) %>%
  summarize(deference = utility[label == playerResponse] != max(utility))

d.deference <- d.by_player_metrics %>% 
  rename(roundID = "_id") %>% 
  left_join(trial_deference)
```

```{r}
d.deference %>% filter(!is.na(deference)) %>%
  ggplot(aes(x = trialNum, y = as.numeric(deference), color = condition)) + 
  geom_smooth(method = "lm") + 
  geom_jitter(width = .1, height = .1, alpha = .05) +
  facet_grid(.~languageCondition)+ scale_color_bay() + theme_jmank()
```

## Post-Test
```{r post-test}

## Simple Distributions
### Individual Points
```{r, fig.height=3, fig.width=5}
d.by_player_metrics %>%
  group_by(languageCondition, condition, playerId) %>%
  summarize(playerPoints = sum(playerUtility)) %>%
  ggplot(aes(x = languageCondition, y = playerPoints, color = condition)) + 
  geom_point(position=position_jitterdodge(dodge.width=.5, jitter.width = .1), alpha = .25) +
  stat_summary(fun.data = "mean_cl_boot", position=position_dodge(width=.5)) + scale_color_bay() + theme_jmank() + theme(legend.position = "bottom")
```

### Game Points

@@

#Points per individual (per trial)
